Community-Conditioned Language Models

### 2020-11-12 paper/paper.tex
lmcc and cclm ppl plots

\begin{figure}
  \begin{tikzpicture}
  \begin{axis}[]
  \addplot[
    scatter, only marks,
    font=\tiny,
    scatter src=explicit symbolic,
    scatter/classes={
      general-interest={mark=*, blue},
      videogames={mark=*, red},
      technology={mark=*, green},
      sports={mark=*, cyan},
      female-focused={mark=*, magenta},
      other={mark=o, black},
      different={mark=x}
    },
    %mark size=1pt,
    %nodes near coords*={\community},
    %visualization depends on={value \thisrow{community} \as \community}
  ] table [x=snap, y=lstm-3-1, meta=meta] {floats/comm_sim.csv};
  \end{axis}
  \end{tikzpicture}
  \caption{Pairwise cosine similarity between community vectors for 
    the membership-based embedding (x-axis) and
  the LSTM CCLM embedding with $c=1$ (y-axis). 
  Pairs from the same category are colored according to Figure~\ref{fig:comm-pca}.
  We also mark pairs from different (\texttimes) and pairs where one or both
  communities belong to the ``Other'' category (\textbigcircle).
  }
  \label{fig:pairwise-comm-sim}
\end{figure}

@@

\begin{figure*}
\begin{tikzpicture}
  \confusiongroupplot{floats/lstm-3-1_comm_infer_confusion.csv}{floats/transformer-3-3_comm_infer_confusion.csv}
\end{tikzpicture}
\caption{LMCC confusion matrices for the best LSTM (left, $c=1$) and transformer (right, $c=3$) models.}
\label{fig:confusion}
\end{figure*}

@@

TODO: scatterplot/r2 between LMCC and CCLM perplexity  ---> no correlation.

@@

TODO: show a scatter plot, compute r2 --> almost perfect correlation

>>>>

\begin{figure}
  \pairwisecommsim{lstm-3-1} 
  \caption{Pairwise cosine similarity between community vectors for 
    the membership-based embedding (x-axis) and
  the LSTM CCLM embedding with $c=1$ (y-axis). 
  Pairs from the same category are colored according to Figure~\ref{fig:comm-pca}.
  We also mark pairs from different (\texttimes) and pairs where one or both
  communities belong to the ``Other'' category (\textbigcircle).
  }
  \label{fig:pairwise-comm-sim}
\end{figure}

@@

%\begin{figure*}
%\begin{tikzpicture}
  %\confusiongroupplot{floats/lstm-3-1_comm_infer_confusion.csv}{floats/transformer-3-3_comm_infer_confusion.csv}
%\end{tikzpicture}
%\caption{LMCC confusion matrices for the best LSTM (left, $c=1$) and transformer (right, $c=3$) models.}
%\label{fig:confusion}
%\end{figure*}

@@

  %\begin{tikzpicture}
  %\pplscatter{lstm-3-1_lmcc}{lstm-3-1_cclm}
  %\end{tikzpicture}

\begin{figure}
  \pplscatter{lstm-3-1_cclm}{lstm-3-1_lmcc}
  \caption{%
    Mean CCLM (x-axis) and LMCC (y-axis) perplexity per community (Pearson's r = \num{0.30}, p = \num{0.0444}).
    Shown here for the LSTM model with $c = 1$, but other models exhibit similar behavior.
  }
  \label{fig:cclm_lmcc_ppl}
\end{figure}

@@

\begin{figure}
  \pplscatter{lstm-3-1_lmcc}{transformer-3-3_lmcc}
  \caption{%
    Mean CCLM perplexity per community for the best LSTM ($c = 1$) and transformer ($c = 3$) models
    (Pearson's r = \num{0.99} p < \num{0.0001}).
  }
  \label{fig:lmcc_ppl}
\end{figure}

### 2020-11-12 paper/plot_macros.tex
lmcc and cclm ppl plots

>>>>

\newcommand{\pairwisecommsim}[1]{%
  \begin{tikzpicture}
  \begin{axis}[]
  \addplot[
    scatter, only marks,
    font=\tiny,
    scatter src=explicit symbolic,
    scatter/classes={
      general-interest={mark=*, blue},
      videogames={mark=*, red},
      technology={mark=*, green},
      sports={mark=*, cyan},
      female-focused={mark=*, magenta},
      other={mark=o, black},
      different={mark=x}
    },
  ] table [x=snap, y=#1, meta=meta] {floats/comm_sim.csv};
  \end{axis}
  \end{tikzpicture}
}

\newcommand{\pplscatter}[2]{%
  \begin{tikzpicture}
  \begin{axis}[]
  \addplot[
    only marks, black,
  ] table [x=#1, y=#2] {floats/cclm_lmcc_ppl.csv};
  \end{axis}
  \end{tikzpicture}
}
